XOR-Some Prolific Pilot 2

### 2021-04-28 analysis/xor-some-prolific-pilot2.Rmd
tweak exclusions, add low completion times, xor prior responses check

#  summarize(timeCounts = count(timeSpent) / d_native %>% )
ggplot(data = overall_timeSpent, aes(y=timeSpent, alpha = 0.7)) +
  geom_boxplot() +
  ggtitle("Overall time participants took in mins")
```
```{r}
d_main <- d_native %>% select(-age, -botresponse, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent) %>%
  filter(trial_name != "example")
d_exmpl <- d_native %>% select(-age, -botresponse, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent) %>%
  filter(trial_name == "example")
d_critical <- d_main %>% filter(condition == "critical")
```

@@

Next, we exclude participants based on their ratings in the main trials: Participants who gave all responses within the range of 10 and participants who failed more than 0.2 of the comprehension questions are excluded from analysis. 
Participants who failed all example trials are excluded, as well. 
The bot check trial is not considered for exclusions. 
```{r exclusions}
# get participants failing example trials
d_exmpl <- d_exmpl %>% group_by(submission_id) %>% 
  mutate(example_condition = ifelse(grepl("as certainly true", question), "true", 
                                    ifelse(grepl("as certainly false", question), "false",
                                           "uncertain")),
         passed_example_trial = case_when(example_condition == "true" ~ response >= 80,
                                    example_condition == "false" ~ response <= 20,
                                    example_condition == "uncertain" ~ response >= 30),
       #  check if all trials passed
         passed_example = case_when(sum(passed_example_trial) == 0 ~ FALSE,
                                    TRUE ~ TRUE)
         ) %>% filter(passed_example == F)

cat("Subjects failing the example trials: ", d_exmpl %>% distinct(submission_id) %>% pull() %>% length())

# apply exclusion criteria to main trials
# check range of responses per participant
d_main_fail <- d_main %>% group_by(submission_id) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
cat("Subjects providing the same ratings throughout the trials: ", d_main_fail %>% distinct(submission_id) %>% pull() %>% length())

# get participants failing comprehension questions
d_test <- d_test %>%
  group_by(submission_id) %>%
  mutate(passed_filler_trial = case_when(test_condition == "true" ~ response >= 70,
                                   test_condition == "false" ~ response <= 40,
                                   test_condition == "uncertain" ~ response %in% (0:90)),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         ) %>%
  filter(passed_filler == F)

cat("Subjects failing the comprehension trials: ", d_test %>% distinct(submission_id) %>% pull() %>% length())

# put it all together
d_full_clean <- anti_join(d_main, d_main_fail, by = "submission_id")
d_full_clean <- anti_join(d_full_clean, d_exmpl, d_test, by = "submission_id")
d_full_clean <- anti_join(d_full_clean, d_test, by = "submission_id")

cat("Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```

@@

```
```{r}
# check whether the ratings in the two prior questions are the same in xor 
d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  filter(block == "prior", main_type == "xor") %>%
  mutate(priorQ_nr = rep(c(1,2), 396)) -> d_xor_priors
d_xor_priors %>% group_by(priorQ_nr, prior_class) %>%
  summarise(mean = mean(response)) -> d_xor_priors_summary
d_xor_priors %>%
  ggplot(., aes(x = as.factor(priorQ_nr), y = response )) +
  geom_point(size = 2, alpha = 0.6, position = position_jitter(width = 0.1)) +
  geom_point(data = d_xor_priors_summary, aes(x = as.factor(priorQ_nr), y = mean), color = "red", size = 3) +
  ylab("Responses to prior questions") +
  xlab("First vs Second prior question for high vs low prior conditions") +
  facet_wrap(~as.factor(prior_class)) # get ratings from the respective trials only

@@

```{r, results='hide'}
# some, maximal model with interactions and maximal REs
model_some <- brm(
  target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

#### Smaller models with raw data to check for collinearity 
Models on raw data with only one predictor: 
```{r, results='hide'}
# xor
model_xor_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.92),
  cores = 4,
  iter = 3000
)
```

@@

With two predictors:
```{r, results='hide'}
# xor
model_xor_pri_comp <- brm(
  target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_pri_rel <- brm(
  target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.92),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_rel_comp <- brm(
  target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_pri_comp <- brm(
  target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_pri_rel <- brm(
  target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_rel_comp <- brm(
  target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

#### Stats on z-scored data
The same stats (full, one predictor, to predictors) on z-scored data:
```{r, results='hide'}
# xor, maximal model with interactions and maximal REs on z-scored data
model_xor_zScored <- brm(
  target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some, maximal model with interactions and maximal REs
model_some_zScored <- brm(
  target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

#### Smaller models with z-scored data
```{r, results='hide'}
# xor
model_xor_zScored_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

With two predictors:
```{r, results='hide'}
# xor
model_xor_zScored_pri_comp <- brm(
  target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_pri_rel <- brm(
  target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_rel_comp <- brm(
  target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_pri_comp <- brm(
  target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_pri_rel <- brm(
  target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_rel_comp <- brm(
  target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

# xor, maximal model with interactions and maximal REs
model_xor_cat <- brm(
  response ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_wide_cat %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
model_some_cat <- brm(
  response ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_wide_cat %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

# xor, maximal model with interactions and maximal REs
model_xor_cat_zScored <- brm(
  response_centered ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_wide_cat_zScored %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
model_some_cat_zScored <- brm(
  response_centered ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
  data = d_critical_wide_cat_zScored %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

>>>>

#  summarize(timeCounts = count(timeSpent) / d_native %>% )
ggplot(data = overall_timeSpent, aes(y=timeSpent, alpha = 0.7)) +
  geom_boxplot() +
  ggtitle("Overall time participants took in mins")
```

Investigate very fast completion times:
```{r}
 d_native %>% mutate(timeSpent = round(timeSpent, 2)) %>%
  filter(timeSpent < 8) -> fast_completions

# check if their responses look somehow peculiar
fast_completions %>%
  ggplot(., aes(x = response)) +
  geom_histogram()

cat("number of fast-responders (below 8 mins):", fast_completions %>% distinct(submission_id) %>% pull() %>% length())
```
Data frames preparation:
```{r}
d_main <- d_native %>% select(-age, -botresponse, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent) %>%
  filter(trial_name != "example")
d_exmpl <- d_native %>% select(-age, -botresponse, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent) %>%
  filter(trial_name == "example")
d_critical <- d_main %>% filter(condition == "critical")
```

@@

Next, we exclude participants based on their ratings in the main trials: Participants who gave all responses within the range of 10 and participants who failed more than 0.2 of the comprehension questions are excluded from analysis. 
Participants who failed all example trials are excluded, as well. 
The bot check trial is not considered for exclusions. 
```{r exclusions}
# get participants failing example trials
d_exmpl_fail <- d_exmpl %>% group_by(submission_id) %>% 
  mutate(example_condition = ifelse(grepl("as certainly true", question), "true", 
                                    ifelse(grepl("as certainly false", question), "false",
                                           "uncertain")),
         passed_example_trial = case_when(example_condition == "true" ~ response >= 80,
                                    example_condition == "false" ~ response <= 20,
                                    example_condition == "uncertain" ~ response >= 30),
       #  check if all trials passed
         passed_example = case_when(sum(passed_example_trial) == 0 ~ FALSE,
                                    TRUE ~ TRUE)
         ) %>% filter(passed_example == F)

cat("Subjects failing the example trials: ", d_exmpl_fail %>% distinct(submission_id) %>% pull() %>% length())

# apply exclusion criteria to main trials
# check range of responses per participant
d_main_fail <- d_main %>% group_by(submission_id) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
cat(" Subjects providing the same ratings throughout the trials: ", d_main_fail %>% distinct(submission_id) %>% pull() %>% length())

# get participants failing comprehension questions
d_test <- d_test %>%
  group_by(submission_id) %>%
  mutate(passed_filler_trial = case_when(test_condition == "true" ~ response >= 70,
                                   test_condition == "false" ~ response <= 40,
                                   test_condition == "uncertain" ~ response %in% (0:90)),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         )

d_test_fail <- d_test %>% 
  filter(passed_filler == F)

cat(" Subjects failing the comprehension trials: ", d_test_fail %>% distinct(submission_id) %>% pull() %>% length())

# plot by-participant means on comprehension questions, and mark red excluded points, 
# to see if the participants performed in a peculiar way
d_test %>% 
  group_by(submission_id, main_type, test_condition) %>%
  mutate(subj_mean = mean(response)) %>%
  ggplot(., aes(x = test_condition, y = subj_mean)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
  geom_point(data = . %>% filter(passed_filler == F), aes(x = test_condition, y = subj_mean), color = "red", 
             size = 2) +
  facet_wrap(~main_type) +
  ggtitle("Red points mark subject response means for subjects\nwith a mean comprehension question accuracy < 0.8")
```

```{r}
# put it all together
d_full_clean <- anti_join(d_main, d_main_fail, by = "submission_id")
d_full_clean <- anti_join(d_full_clean, d_exmpl_fail, d_test, by = "submission_id")
d_full_clean <- anti_join(d_full_clean, d_test_fail, by = "submission_id")

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```

Check exclusions if applying exclusion ranges as suggested by Bob -- then almost twice as many participants are excluded based on their comprehension questions performance (I believe mainly due to a lower bound on correct responses in the uncertain questions). 
```{r}
# true comprehension questions: 50-100
# uncertain comprehension questions: 25-75
# false comprehension questions: 0-50
# get participants failing example trials

d_exmpl2 <- d_exmpl %>% group_by(submission_id) %>% 
  mutate(example_condition = ifelse(grepl("as certainly true", question), "true", 
                                    ifelse(grepl("as certainly false", question), "false",
                                           "uncertain")),
         passed_example_trial = case_when(example_condition == "true" ~ response >= 50,
                                    example_condition == "false" ~ response <= 50,
                                    example_condition == "uncertain" ~ response %in% (25:75)),
       #  check if all trials passed
         passed_example = case_when(sum(passed_example_trial) == 0 ~ FALSE,
                                    TRUE ~ TRUE)
         ) %>% filter(passed_example == F)

cat("Subjects failing the example trials: ", d_exmpl2 %>% distinct(submission_id) %>% pull() %>% length())

# apply exclusion criteria to main trials
# check range of responses per participant
d_main_fail <- d_main %>% group_by(submission_id) %>%
  mutate(passed_main = case_when(max(response) - min(response) <= 10 ~ FALSE,
                                 TRUE ~ TRUE)
         ) %>% filter(passed_main == F)
cat(" Subjects providing the same ratings throughout the trials: ", d_main_fail %>% distinct(submission_id) %>% pull() %>% length())

# get participants failing comprehension questions
d_test2 <- d_test %>%
  group_by(submission_id) %>%
  mutate(passed_filler_trial = case_when(test_condition == "true" ~ response >= 50,
                                   test_condition == "false" ~ response <= 50,
                                   test_condition == "uncertain" ~ response %in% (25:75)),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         )

d_test_fail2 <- d_test2 %>% 
  filter(passed_filler == F)

cat(" Subjects failing the comprehension trials: ", d_test_fail2 %>% distinct(submission_id) %>% pull() %>% length())

```
Now we explore applying exclusion criteria on z-scored data. Here it might make sense to exclude participants whose >=0.8 of responses are more than 2 SD from the mean (?). 
```{r}
# group by extended block, exmpl / filler / critical, maybe polarity of filler exmpl question
# add block extension, put all data together somehow
d_critical_fail_zScored <- d_main %>% 
  mutate(block_extended = ifelse(
    !(ifelse(is.na(critical_question), F, T)), 
    block, 
    ifelse(block %in% c("some", "xor"), "target", str_c(block, "_wUtt", ""))
  )  
  ) %>% 
  filter(!(grepl("test", block_extended))) %>%
  group_by(submission_id, block_extended) %>%
  mutate(subj_block_mean = mean(response),
         subj_block_sd = sd(response),
         response_centered = (response - subj_block_mean)/subj_block_sd,
         # catch the cases where sd is 0 
         response_centered = ifelse(is.na(response_centered), 0, response_centered)) %>%
  ungroup() %>%
  # add by-block SDs, such that participants can be excluded based on being outside 2 SDs on a block
  # or should this be based on by-subject SDs???? 
  group_by(block_extended) %>%
  mutate(block_mean = mean(response),
         block_sd = sd(response),
         passed_main_trial = case_when(abs(response_centered) <= 2*block_sd ~ T,
                                       T ~ F),
         mean_critical_passRate = mean(passed_main_trial))

# get participants failing comprehension questions with z-scored data; here, by-subject SD are used for the exclusion
d_test_fail_zScore <- d_test %>%
  group_by(submission_id, test_condition) %>%
  mutate(
    subj_block_mean = mean(response),
    subj_block_sd = sd(response),
    response_centered = (response - subj_block_mean)/subj_block_sd,
    response_centered = ifelse(is.na(response_centered), 0, response_centered),
    passed_filler_trial = case_when(abs(response_centered) <= 2*subj_block_sd ~ T,
                                   T ~ F),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         )

d_test_fail_zScore <- d_test_fail_zScore %>% 
  filter(passed_filler == F)
```

@@

```
```{r, fig.height=3}
# check whether the ratings in the two prior questions are the same in xor 
d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  filter(block == "prior", main_type == "xor") %>%
  mutate(priorQ_nr = rep(c(1,2), 396),
         unique_ID = paste(submission_id, ID, sep="_")) -> d_xor_priors
d_xor_priors %>% group_by(priorQ_nr, prior_class) %>%
  summarise(mean = mean(response)) -> d_xor_priors_summary

d_xor_priors %>%
  ggplot(., aes(x = as.factor(priorQ_nr), y = response )) +
  geom_point(size = 2, alpha = 0.6, position = position_jitter(width = 0.1)) +
  geom_point(data = d_xor_priors_summary, aes(x = as.factor(priorQ_nr), y = mean), color = "red", size = 3) +
  geom_path(aes(group = "unique_ID"), alpha = 0.6) +
  ylab("Responses to prior questions") +
  xlab("First vs Second prior question for high vs low prior conditions") +
  facet_wrap(~as.factor(prior_class)) + # get ratings from the respective trials only 
  ggtitle("Xor prior question ratings.\nLines indicate the two responses provided by one participant for a specific item.")
```

@@

```{r, results='hide'}
# some, maximal model with interactions and maximal REs
model_some <- brm(
  bf(target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

#### Smaller models with raw data to check for collinearity 
Models on raw data with only one predictor: 
```{r, results='hide'}
# xor
model_xor_prior <- brm(
  bf(target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_comp <- brm(
  bf(target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_rel <- brm(
  bf(target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_rel <- brm(
  bf(target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_prior <- brm(
  bf(target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_comp <- brm(
  bf(target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.92),
  cores = 4,
  iter = 3000
)
```

@@

With two predictors:
```{r, results='hide'}
# xor
model_xor_pri_comp <- brm(
  bf(
  target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
  decomp = "QR"
  ),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_pri_rel <- brm(
  bf(target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.92),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_rel_comp <- brm(
  bf(target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_pri_comp <- brm(
  bf(target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_pri_rel <- brm(
  bf(target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_rel_comp <- brm(
  bf(target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

#### Stats on z-scored data
The same stats (full, one predictor, to predictors) on z-scored data:
```{r, results='hide'}
# xor, maximal model with interactions and maximal REs on z-scored data
model_xor_zScored <- brm(
  bf(target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some, maximal model with interactions and maximal REs
model_some_zScored <- brm(
  bf(target ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

#### Smaller models with z-scored data
```{r, results='hide'}
# xor
model_xor_zScored_prior <- brm(
  bf(target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_comp <- brm(
  bf(target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_rel <- brm(
  bf(target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_rel <- brm(
  bf(target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_prior <- brm(
  bf(target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_comp <- brm(
  bf(target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

With two predictors:
```{r, results='hide'}
# xor
model_xor_zScored_pri_comp <- brm(
  bf(target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_pri_rel <- brm(
  bf(target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_zScored_rel_comp <- brm(
  bf(target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_pri_comp <- brm(
  bf(target ~ prior*competence + 
    (1 + prior*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_pri_rel <- brm(
  bf(target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_zScored_rel_comp <- brm(
  bf(target ~ relevance*competence + 
    (1 + relevance*competence || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_zScored_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

# xor, maximal model with interactions and maximal REs
model_xor_cat <- brm(
  bf(response ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide_cat %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
model_some_cat <- brm(
  bf(response ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide_cat %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

# xor, maximal model with interactions and maximal REs
model_xor_cat_zScored <- brm(
  bf(response_centered ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide_cat_zScored %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
model_some_cat_zScored <- brm(
  bf(response_centered ~ prior*competence*relevance + 
    (1 + prior + competence + relevance || submission_id) +
    (1 | title),
    decomp = "QR"),
  data = d_critical_wide_cat_zScored %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```
